### 2019-02-01 results.tex
need diamoinds below whiskers

\subsection{Benchmark Applications and Training/Testing  Datasets}
The machine learning applications that we use to evaluate Seneca 
are shown in Table~\ref{tab:bmarks}, each with 
a brief description.
Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
%logorithm
of Payton Manning's wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
We use the first 6 years as the training set and the last 2 years as the testing set.
We use a cross-validation horizon (sliding window) of 1-year, 
and a period (sliding pace) 
of 180 days.  As such, Seneca performs three cross-validations for each 2-year testing range.

@@

Prophet expects multiple hyperparameters: \textit{growth} specifies linear or logistic trend model growth; \textit{prior scale} indicates the strength of the 
sparse prior probability~\cite{ref:sparse_prior}. 
There are three prior scale hyperparameters for change point, holidays, and seasonality. 
Since Prophet uses a Fourier sum to estimate seasonality, 
the \textit{fourier order} is the number of terms in the partial Fourier 
sum. \textit{Seasonality mode} indicates that the effect of seasonality is either 
multiplicative or additive. Finally, the width of uncertainty intervals 
can be set using the hyperparameter \textit{interval width}.

@@

Multi-Regression is a regression application 
developed by the authors of 
an IoT project~\cite{iot-cpu} that
predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures (e.g. for use in 
precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

A hyperparameter configuration for this application is a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
For this application,
we assume the default parameterization is the set of all $N$ input time series (8 in this case).
The test dataset for this application is a time series of the outdoor temperature (ground truth) 
over the same period.  The application makes predictions for each of these outdoor temperatures
using the model constructed from the training set
and computes the mean square error across predicted and ground truth value pairs.

@@

\subsection{Empirical Methodology}
To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
For tuning performance, we use mean squared error (MSE) for regression tasks 
and percentage accuracy for
classification tasks. The default configuration that we 
consider for each application is described above.
We report results for the default, the best (Seneca's recommendation), 
and the worst performing configurations.  Seneca considers all possible combinations 
of the hyperparameter settings specified in the configuration, uses them
to train, test, and evaluate models for each. 
The default results represents a configuration that a novice or first time 
user might employ when using these applications
as a ``black box''.  The worst performing scenario shows how bad the results can be
when parameters are poorly tuned.  Finally, the best configuration 
is the one that results from tuning they hyperparameters for the test/train split
that Seneca considers.

@@

We also experiment with different memory configurations for Seneca functions in AWS Lambda.  
We evaluate
the performance and cost of allocating the maximum memory for each and for automatically optimizing 
memory use using Seneca. We assume that all combinations hyperparameter settings use the 
same maximum amount of memory across functions; we 
have verified that this assumption holds for the applications and datasets that
we consider herein.
We plan to consider applications for which hyperparameter settings require 
different maximum amounts of memory as part of future work.

@@

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better)
for these applications 
for the entire hyperparameter 
search space. The central rectangle covers the interquartile range (IQR), 
which is defined as the range of data 
points from first quartile to third quartile (Q3 - Q1). 
The upper whisker extends to the last datum less 
than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater 
than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers 
and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
the model using the default settings of hyperparameter. 
The difference between red notch of lowest data 
point is the improvement brought about by the use of Seneca. 
The red notch marks the MSE of the default hyperparameterization.
Each is located near the 
From the location of red notch, we can see the MSE metrics 
first quartile value indicating that there is significant 
potential room for improvement in MSE. The box plot also illustrates 
that the best MSE of Prophet and multivariate regression are among the outliers, 
indicating that a comprehensive search is critical to finding the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}

>>>>

\subsection{Benchmark Applications and Training/Testing  Datasets}

The machine learning applications that we use to evaluate Seneca are shown in
Table~\ref{tab:bmarks}, each with a brief description.
Prophet~\cite{ref:prophet} is a time series analysis library built and
maintained by Facebook and the open-source community. The input dataset is a
time series of view counts
%logorithm
of Payton Manning's wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016.
The dataset exhibits both seasonality and a holiday effect (e.g. around the
super bowl games).  We use the first 6 years as the training set and the last
2 years as the testing set.  We use a cross-validation horizon (sliding
window) of 1-year, and a period (sliding pace) of 180 days.  As such, Seneca
performs three cross-validations for each 2-year testing range.

@@

Prophet accepts the following hyperparameters: 
\textit{growth} specifies linear or
logistic trend model growth; \textit{prior scale} indicates the strength of
the sparse prior probability~\cite{ref:sparse_prior}.  There are three prior
scale hyperparameters for change point, holidays, and seasonality.  Since
Prophet uses a Fourier sum to estimate seasonality, the \textit{fourier order}
is the number of terms in the partial Fourier sum. \textit{Seasonality mode}
indicates that the effect of seasonality is either multiplicative or additive.
Finally, the width of uncertainty intervals can be set using the
hyperparameter \textit{interval width}.

@@

Multi-Regression is a regression application developed by the authors of an
IoT project~\cite{iot-cpu} that predicts outdoor temperature from the
processor temperature of single board computers (SBCs).  The technique uses
multiple linear regression models computed from time series of processor
temperature measurements, to predict outdoor microclimate temperatures (e.g.
for use in precision agriculture applications such as irrigation control and
frost protection).  The training dataset consists of eight input time series
(one per SBC, each containing 5-minute measurements) from April 5th, 2018 to
Dec. 10th, 2018.  In addition, for each regression there is a single ``ground
truth'' time series of measurements taken from a temperature sensor.

A hyperparameter configuration for this application is a subset of input SBC
time series.  That is, the ``best'' regression (in terms of lowest regression
error) comes from some subset of  the SBC series when used as explanatory
variables for a regression of the ground truth series.  Seneca considers all
\texttt{$2^N - 1$} potential subsets (for $N$ SBC time series).  For this
application, we assume the default parameterization is the set of all $N$
input SBC time series (8 in this case) as explanatory variables.  The test
dataset for this application is a time series of the outdoor temperature
(ground truth) over the same period.  The application makes predictions for
each of these outdoor temperatures using the model constructed from the
training set and computes the mean square error across predicted and ground
truth value pairs.

@@

\subsection{Empirical Methodology}

To evaluate Seneca, we measure tuning performance, application execution time,
and monetary cost.  For tuning performance, we use mean squared error (MSE)
for regression tasks and percentage accuracy for classification tasks. The
default configuration that we consider for each application is described
above.  We report results for the default, the best (Seneca's recommendation),
and the worst performing configurations.  Seneca considers all possible
combinations of the hyperparameter settings specified in the configuration,
uses them to train, test, and evaluate models for each.  The default results
represents a configuration that a novice or first time user might employ when
using these applications as a ``black box''.  The worst performing scenario
shows how bad the results can be when parameters are poorly tuned.  Finally,
the best configuration is the one that results from tuning they
hyperparameters for the test/train split that Seneca considers.

@@

We also experiment with different memory configurations for Seneca functions
in AWS Lambda.  The pricing model for AWS Lambda charges the account under
which a computation executes based on the product of its execution time and
the size of the memory the account owner chooses to configure.  If the
application exceeded the configured memory, it is terminated.  
%Thus, the cost
%optimal configuration is one in which the allocated memory is just large
%enough to run the application, and no larger, assuming the size of the memory
%does not affect execution runtime.  
Seneca includes an probing
mechanism that attempts to ``learn'' this memory size for a given
application that minimizes its ecxecution cost.  Note that because AWS Lambda
does not provide a way to control the speed of the processor that ultimately
executes each Lambnda function, memory size is the only available cost tuning
parameter.

We evaluate the performance and cost of allocating the maximum memory versus
Seneca's automatic memory size optimizer. To do so, we assume that all
combinations hyperparameter settings use the same maximum amount of memory
across all function executions. We have verified that this assumption holds
for the applications and datasets that we consider herein however we plan to
consider applications for which hyperparameter settings require different
maximum amounts of memory as part of future work.

@@

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better)
for these applications 
for the entire hyperparameter search space. The central rectangle covers the interquartile range (IQR), 
which is defined as the range of data 
points from first quartile to third quartile (Q3 - Q1). 
The upper whisker extends to the last datum less 
than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater 
than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers 
and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
the model using the default settings of hyperparameter. 
The difference between red notch of lowest data 
point is the improvement brought about by the use of Seneca. 
The red notch marks the MSE of the default hyperparameterization.
Each is located near the 
From the location of red notch, we can see the MSE metrics 
first quartile value indicating that there is significant 
potential room for improvement in MSE. The box plot also illustrates 
that low MSE hyperparametrizations are often rare in the hyperparameter space.
Note that for Prophet and Multi-regression, the number of parameterizations that
yield an MSE lie below the low whisker is small and that the best MSE is
always more than $2 * IQR$ below the Q1 quartile.  Thus a comprehensive
exploration of the hyperparameter space is warranted from the perspective of
minimizing the MSE.

%of Prophet and multivariate regression are among the outliers, 
%indicating that a comprehensive search is critical to finding the best configurations.

%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}
